%essential for ref.
\renewcommand{\refname}{}
\begin{thebibliography}{}
\vspace*{-1cm}
%


\bibitem{im1} 
V. Pedroni,
\textit{Circuit design and simulation with VHDL.},2017. Cambridge [EE. UU.]: The MIT Press, 2010.

\bibitem{im2} 
"VHDL Tutorial: Learn by Example",
\textit{Esd.cs.ucr.edu,} 2017. [Online]. Available: \texttt{http://esd.cs.ucr.edu/labs/tutorial/.} [Accessed: 01- Aug- 2017].

\bibitem{im3} 
"Basys 2 Reference Manual [Reference.Digilentinc]",
\textit{ Reference.digilentinc.com,}  2017. [Online]. Available: \texttt{https://reference.digilentinc.com/reference/programmable-logic/basys-2/ reference-manual.} [Accessed: 05- Aug- 2017].

\bibitem{im4} 
"VHDL for FPGA Design/4-Bit BCD Counter with Clock Enable - Wikibooks, open books for an open world",\textit{ En.wikibooks.org,}  2017. [Online]. Available: \texttt{https://en.wikibooks.org/wiki/VHDL$ _{-}$for$ _{-} $FPGA$ _{-} $Design/4-Bit$ _{-} $BCD$ _{-} $Counter$ _{-} $with$ _{-} $ Clock$ _{-} $Enable}. [Accessed: 07- Aug- 2017].

\bibitem{im5} 
"Counters",\textit{ Csit-sun.pub.ro,}  2017. [Online]. Available: \texttt{http://www.csit-sun.pub.ro/courses /Masterat/Xilinx\textdiscount 20Synthesis\textdiscount20Technology/toolbox.xilinx.com/docsan/xilinx4/data /docs/xst/hdlcode6.html.} [Accessed: 07- Aug- 2017].

\bibitem{im6} 
J. Deschamps, G. Sutter and E. Cant\'{o},
\textit{Guide to FPGA Implementation of Arithmetic Functions.}, Dordrecht: Springer Netherlands, 2012.
\end{thebibliography}
